Part B-2

### 2025-09-07 msca-pf-part-b2-template.tex
fix: use 12pt fonts in part-b2 as well
feat: sync microtype setup

% better typography
\usepackage[activate={true,nocompatibility}, % activate protrusion and font expansion
            final,              % enable microtype, use draft to disable
            tracking=true,
            factor=1100,        % more protrusion
            stretch=10,         % smaller values (default 20, 20) to avoid blurring
            shrink=10]{microtype}
\SetTracking{encoding={*}, shape=sc}{40}

>>>>

% better typography
\usepackage[activate={true,nocompatibility}, tracking=true]{microtype}
